### 2015-02-22 fundamentals/impl.tex
cleaned up the dre intro a bit

Since the \Cyclus simulation paradigm allows discrete agents, based on archetypes
about which the kernel has no knowledge, to enter
the simulation at arbitrary times and
trade in discrete resources that are not defined \textit{a priori},
the logic engine defining resource interaction mechanisms
among agents is crucial. The \gls{DRE} is that critical logic engine on which \Cyclus
simulations are built.
As the \Cyclus supply-demand resolution framework,
the DRE must be able to support arbitrary facilities. Supporting the general
\Cyclus philosophy, facilities are treated as black boxes and a clear
supply-demand communication framework is defined.

>>>>

The \Cyclus simulation paradigm allows discrete agents, based on archetypes
about which the kernel has no knowledge, to enter the simulation at arbitrary
times and trade in discrete resources. These resources are not defined \textit{a
  priori}. Therefore, the logic engine defining resource interaction mechanisms
among agents is crucial. The \gls{DRE} is that critical logic engine on which
\Cyclus simulations are built.  As the \Cyclus supply-demand resolution
framework, the DRE must be able to support arbitrary facilities. Supporting the
general \Cyclus philosophy, facilities are treated as black boxes and a clear
supply-demand communication framework is defined.
